Discussion Draft

### 2020-04-05 doc/Discussion.rmd
kinda fixed 2 locus part in hetC reversal

The common direction of heterochiasmy is female biased, however male biased heterochiasmy examples are not especially rare. Our results are novel from previous examples of male biased heterochiasmy species because the panel of strains have much shorter evolutionary distances. This context gives us insights to sex-specific evolution of recombination rates.  
Male biased heterochiasmy is predicted under the two locus modifier model when XXXX.  <does parameterize cases for male biased heterochiasmy, dependent on the stage of action for the driver (MI or MII) and the linkage status (see table 1 Brandvain and Coop).>

@@

Under the **spindle based** model faster male evolution in male genome wide recombination rates is primarily driven the strength of the spindle assembly checkpoint (SAC) acting on the chromosome structure at metaphase alignment. We will not go into much detail on the mechanism of the SAC, The genes and pathways are will known, we refer the reader to [@laneKauppi2019].

The transition from metaphase to anaphase is irreversible, so all bivalents in the cell have to be aligned correctly to prevent anueploidy.

>>>>

Female biased heterochiasmy is the most common pattern observed, however male biased heterochiasmy is not especially rare [@brandvain2012scrambling]. Our results of male biased heterochiasmy is novel due to the shorter evolutionary distances between the examined strains.

The direction of heterochiasmy under the **two locus modfier model** is dependant on female specific recombination modifer supresses or increases recombination, if the modifer is linked to the driving locus, and the meiotic stage (reduction or equalatoral division) that the driver acts (see Table 1 of @brandvain2012scrambling).

@@

Under the **spindle based** model, faster male evolution of the genome wide recombination rates is primarily driven the strength of the spindle assembly checkpoint (SAC) acting on the chromosome structure at metaphase alignment. We refer the reader to [@laneKauppi2019] for more details on the sAC pathway.

The transition from metaphase to anaphase is irreversible,

so all bivalents in the cell have to be aligned correctly to prevent anueploidy.
